Activity Recognition using Random Forest Algorithm
========================================================

The goal of this project is develop a predict model to identify which activity a person was performed. The data used were from accelerometers on the belt, forearm, arm and dumbell. More specifically, the goal of this project is test if it is possible develop a acurate predict model for this problem using only Random Forest Algorithm [[1]](ftp://131.252.97.79/Transfer/Treg/WFRE_Articles/Liaw_02_Classification%20and%20regression%20by%20randomForest.pdf).

The dataset used in this work was [[2]](http://groupware.les.inf.puc-rio.br/static/WLE/WearableComputing_weight_lifting_exercises_biceps_curl_variations.csv) and the paper that describe the dataset can be found at [[3]](http://groupware.les.inf.puc-rio.br/public/papers/2013.Velloso.QAR-WLE.pdf).

```{r}
set.seed(1234)
options(stringsAsFactors=TRUE)
training <- read.csv("../data/pml-training.csv", header=TRUE)
training$X <- NULL
````

This dataset has `r dim(training)[1]` examples and `r dim(training)[2]` attributes. However, some attributes are irrelevant as predictors, for example: user\_name, raw\_timestamp\_part\_1, raw\_timestamp\_part_2, cvtd\_timestamp, new\_window and num\_window. Therefore, I will remove these attributes from the dataset.

```{r}
f_training <- training
f_training$user_name <- NULL
f_training$raw_timestamp_part_1 <- NULL
f_training$raw_timestamp_part_2 <- NULL
f_training$cvtd_timestamp <- NULL
f_training$new_window <- NULL
f_training$num_window <- NULL
````

Besides, there some attributes with NA values. Random Forest Algorithm can not handle attributes with NA values. Therefore, I removed these attributes from the dataset using the command below:

```{r}
f_training <- f_training[,colSums(is.na(f_training))==0]
````

For some reason, there are some attributes that were imported without values
and as character type. In this case, I removed manually each attribute using the commands
below:

```{r}
f_training$kurtosis_roll_belt <- NULL
f_training$kurtosis_picth_belt <- NULL
f_training$kurtosis_yaw_belt <- NULL
f_training$skewness_roll_belt <- NULL
f_training$skewness_roll_belt.1 <- NULL
f_training$skewness_yaw_belt <- NULL
f_training$max_yaw_belt <- NULL
f_training$min_yaw_belt <- NULL
f_training$amplitude_yaw_belt <- NULL
f_training$kurtosis_roll_arm <- NULL
f_training$kurtosis_picth_arm <- NULL
f_training$kurtosis_yaw_arm <- NULL
f_training$skewness_roll_arm <- NULL
f_training$skewness_pitch_arm <- NULL
f_training$skewness_yaw_arm <- NULL
f_training$kurtosis_roll_dumbbell <- NULL
f_training$kurtosis_picth_dumbbell <- NULL
f_training$kurtosis_yaw_dumbbell <- NULL
f_training$skewness_roll_dumbbell <- NULL
f_training$skewness_pitch_dumbbell <- NULL
f_training$skewness_yaw_dumbbell <- NULL
f_training$max_yaw_dumbbell <- NULL
f_training$min_yaw_dumbbell <- NULL
f_training$amplitude_yaw_dumbbell <- NULL
f_training$kurtosis_roll_forearm <- NULL
f_training$kurtosis_picth_forearm <- NULL
f_training$kurtosis_yaw_forearm <- NULL
f_training$skewness_roll_forearm <- NULL
f_training$skewness_pitch_forearm <- NULL
f_training$skewness_yaw_forearm <- NULL
f_training$max_yaw_forearm <- NULL
f_training$min_yaw_forearm <- NULL
f_training$amplitude_yaw_forearm <- NULL
````

After pre-processing step, the dataset has `r dim(f_training)[1]` examples and `r dim(f_training)[2]` attributes. 